Supporting Information

### 2018-03-13 SupportingInformation.Rmd
inserting \newpage command to get clean table

@@

```{r tab_count_bestcop, echo=F, results='markup'}
knitr::kable(RES_aphid_count$info_ord_copname[,,1], 
             format='pandoc',
             caption = "Aphid_count : best fit copula family for each selective location pair\\label{tab_count_bestcop}",
             booktabs=TRUE
             )
```

@@

```{r tab_pns_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$info_ord_AICw[,,1],
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : AICw for best fit copula family for each selective location pair\\label{tab_pns_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_p_CvM,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$gfc_p_CvM,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : p-values (Cramer-von Mises-based test) for lowest AIC based best fit copula\\label{tab_pns_p_CvM}",
             booktabs=TRUE)
```

@@

## References:

>>>>

<!--
```{r, echo=F}
options(knitr.table.format = "html")
```
-->

@@

```{r tab_count_bestcop, echo=F, results='markup'}
#library(dplyr)
knitr::kable(RES_aphid_count$info_ord_copname[,,1], 
             format='pandoc',
             caption = "Aphid_count : best fit copula family for each selective location pair\\label{tab_count_bestcop}",
             booktabs=TRUE
             )#%>% # only with 'latex'/'html' format
 # kableExtra::kable_styling(latex_options = c("striped","HOLD_position"))
```

@@

\newpage
```{r tab_pns_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$info_ord_AICw[,,1],
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : AICw for best fit copula family for each selective location pair\\label{tab_pns_AICw}",
             booktabs=TRUE)
```

\newpage
```{r tab_pns_p_CvM,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$gfc_p_CvM,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : p-values (Cramer-von Mises-based test) for lowest AIC based best fit copula\\label{tab_pns_p_CvM}",
             booktabs=TRUE)
```

@@

\newpage
## References:
